Which spherical CNN should you use?\\ DeepSphere V2

### 2019-09-03 main.tex
move full tables to appendix

\begin{table}[ht]
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        Deepsphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
        Deepsphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}

\begin{table}[ht]
    \centering
    \begin{tabular}{l|c c c c|c c c c}
     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
    Deepsphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
    Deepsphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428
    \end{tabular}
    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
    \label{tab:SHREC17_retriev}
\end{table}
* add MN40 too? \\
* add improved graph results too? \\

@@

\begin{table}[!ht]
\begin{tabular}{l|c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
        \cmidrule(lr){2-5}
        \multicolumn{1}{l}{Method} & BG & TC & AR & mean \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        Jiang et al. & 97 & 94 & 93 & 94.67\\
        Jiang (bsize 64) & 95.2 & 93.9 & 95.7 & 94.95\\
        % 328'339
        Cohen et al. (S2R) & 97.3 & 97.8 & 97.3 & 97.5\\
        Cohen et al. (R2R) & 97.4 & 97.9 & 97.8 & 97.7\\ \hline
        DS (ico) & $98.2\pm 0.5$ & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $97.8\pm 0.3$ \\
        %DS (non-weighted) & 99.8 & 73.3 & 90.2 & 87.81 & 79.29 & 97.93 & 88.61 & 30ms & 3h50m\\
        DS (non-weighted) & $99.7\pm 0.1$ & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $87.8\pm 0.5$ \\ \hline
        % DS (non-weighted) & 99.6 & 66.6 & 96.1 & 87.41\\ \hline
        % 12'926'432
        DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

\begin{table}[!ht]
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        Jiang (bsize 64) & 11.08 & 65.21 & 38.41 & 10.2 ms & 10h14m\\
        % 328'339
        Cohen et al. (S2R) & - & -& 68.6 & - & - \\
        Cohen et al. (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (ico) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 ms & 25h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 ms & 13h \\ \hline
        % DS (non-weighted) & 83.66 & 97.57 & 90.62 & 30ms & 13h\\ \hline
        % 12'926'432
        % non-weighted: accuracy (99.28, 33.60, 93.56, mean: 75.4819);AP (46.15, 93.87, mean: 70.01)
        % weighted:        accuracy (96.52, 97.13, 97.59, mean: 97.08); AP (49.71, 89.23, mean: 69.47)
        DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as wel, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}

* trade off between AP and accuracy in the case of TC class, it seems.\\
* change base, influence\\
*

@@

\subsubsection*{dense regression - future temperature estimation}
* Task is to find the temperature at day T, knowing the temperature of the 5 previous days.\\
* Goal is to change the order of the chebyshev filter to find the influence of the structure.\\
* order 0 is the same as time series, as the pixel have no information of its neighborhood.\\
* increasing order is good until threshold.\\
* The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference.\\

\begin{table}[!ht]
    \centering
    \begin{minipage}{0.48\linewidth}
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 10.88 & 2.42 & 0.896\\
        1 & 8.91 & 2.20 & 0.906\\
        4 & 8.20 & 2.11 & 0.919\\
        9 & 8.38 & 2.12 & 0.915\\
    \end{tabular}
    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
    \label{tab:future_results}
    \end{minipage}
    \hfill
    %~\\[1cm]
    \begin{minipage}{0.48\linewidth}
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        1 & 134.01 & 10.51 & -0.319\\
        4 & 129.48 & 10.31 & -0.274\\
        9 & 141.68 & 10.82 & -0.389\\
    \end{tabular}
    \caption{Baseline: testing with the present day (T-1) instead of the future day T}
    \label{tab:present_results}
    \end{minipage}
\end{table}

\subsubsection*{global regression - day in year estimation}
* days represented by a sine to represent the periodic nature of the year.\\
* task too easy, features already periodic\\
* structure is still helping\\

@@

\section{Experiments details}
* Network architecture and details
\subsection{3D object Recognition}
\subsubsection*{HEALPix}
HEALPix sampling, input signal at Nside = 32

@@

\subsection{climate event detection}
\subsubsection*{Icosahedron}
icosahedron sampling, level-5 resolution

@@

30 epochs
\subsubsection*{Jiang Icosahedron}
encoder:\\
\begin{dmath}
    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
\end{dmath}
decoder:\\
\begin{dmath}
    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
\end{dmath}
number of parameters: 590'976  % more feat is 16 times more

@@

250 epochs with no augmentation
\subsection*{Dense}

>>>>

\subsubsection*{SHREC17}

\begin{table}[ht]
    \centering
    \begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{1}{c}{size} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-4} \cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & F1-score & mAP & params & inference [ms] & training \\ \hline
        \cite{cohen_spherical_2018} & 78.85 & 67.6 & 1.4M & 38 & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        \cite{esteves_learning_2017} & 79.36 & 68.5 & 500k & 10 & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.36 & 66.5 & 190k & 1 & 2h33m \\
        DeepSphere \emph{HEALPix} & 80.65 & 68.6 & 190k & 1 & 48m\\
        DeepSphere \emph{Improved HEALPix} & ? & ? & 190k & ? & ?
    \end{tabular}
    \caption{Performance of different models for SHREC'17 task. F1-score computed with sklearn, mAP from the official script of the competition.}
    \label{tab:SHREC17_class}
\end{table}

* inference speed = time for a single instance to do a single training pass\\
* training speed = time for the neural net to train to peak performance\\

* add improved graph results too? ==> improved graph unnecessary (main information in low frequency) \\
* diminish resolution ==> no change in result until nside=8, no change for high resolution => info in the low freq\\
* same conclusion, anisotropy unnecessary cost to pay\\
* Limited by representation of data?\\

\subsubsection*{ModelNet 40}
* in appendix now\\

@@

\begin{table}[!ht]
\begin{tabular}{l|c c c c}
        \multicolumn{1}{l}{} & Accuracy & Average Precision & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-2} \cmidrule(lr){3-3} \cmidrule(lr){4-5} 
        \multicolumn{1}{l}{Method} & mean & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94.67 & - & - & -\\
        \cite{jiang_spherical_2019} \emph{rerun} & 94.95 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.5 & 68.6 & - & -\\
        \cite{cohen_gauge_2019} (R2R) & 97.7 & 75.9 & - & -\\ \hline
        % unknown
        DeepSphere (weighted) & $97.8\pm 0.3$ & $77.15\pm 1.94$ & 25 ms & 25h \\
        DeepSphere (non-weighted) & $87.8\pm 0.5$ & $89.16\pm 1.37$ & 30 ms & 13h\\
        % 12'926'432
    \end{tabular}
    \caption{Climate pattern segmentation mean accuracy (\%), mean Average Precision (\%) and speed for different models run on the icosahedron dataset from \cite{jiang_spherical_2019}}
\end{table}

* Jiang rerun with a batch size of 64 instead of 256 due to memory limit.\\
* cross entropy loss between parenthesis\\
* 5 runs for each loss to obtain mean and std\\

* trade off between AP and accuracy in the case of TC class, it seems.\\
* change base, influence?\\

* full dataset not enough memory to run a correct model

@@

\paragraph*{dense regression - future temperature estimation}~\\
* Task is to find the temperature at day T, knowing the temperature of the 5 previous days.\\
* Goal is to change the order of the chebyshev filter to find the influence of the structure.\\
* order 0 is the same as time series, as the pixel have no information of its neighborhood.\\
* increasing order is good until threshold.\\
* The NN indeed predicts the correct temperature at day T, and not day T-1 (baseline) even though there is small difference.\\

\paragraph*{global regression - day in year estimation}~\\
* days represented by a sine to represent the periodic nature of the year.\\
* task too easy, temperature feature already periodic ==> second experiment with only precipitation feature\\
* structure is still helping\\

\begin{table}[!ht]
    \centering
    \begin{tabular}{c|ccc}
        order & future temp & day (temperature) & day (precipitations) \\ \hline 
        0 & 0.896 & 0.881 & - 0.920\\
        4 & 0.919 & 0.969 & 0.597\\
    \end{tabular}
    \caption{R2 coefficient for different tasks on the GHCN dataset}
    \label{tab:GHCN_results}
\end{table}

@@

\section{Experiments details}
* Network architecture and details
\subsection{3D object Recognition}
\subsubsection*{Detailed results}
\paragraph*{SHREC17}
\begin{table}[!ht]
    \centering
    \begin{tabular}{l|c c r r}
        \multicolumn{1}{l}{} & \multicolumn{2}{c}{performance} & \multicolumn{2}{c}{speed}\\
        \cmidrule(lr){2-3} \cmidrule(lr){4-5}
        \multicolumn{1}{l}{Method} & Accuracy & F1-score & inference & training \\ \hline
        Cohen \emph{s2cnn} & - & - & 38ms & 50h\\
        % Cohen \emph{s2cnn\_simple} & 78.59 & 78.85 & 400k & 12ms & 32h\\
        Esteves \emph{sphericalcnn} & 79.18 & 79.36 & 9.8ms & 2h52\\ \hline
        DeepSphere \emph{Equiangular} & 79.25 & 79.36 & 0.98ms & 2h33m \\
        DeepSphere \emph{HEALPix} & 80.42 & 80.65 & 1.0ms & 48m\\
        DeepSphere \emph{Improved HEALPix} & 80.76 & & & 
    \end{tabular}
    \caption{Performance of different models}
    \label{tab:SHREC17_class}
\end{table}

\begin{table}[!ht]
    \centering
    \begin{tabular}{l|c c c c|c c c c}
     & \multicolumn{4}{c|}{micro (label average)} & \multicolumn{4}{c}{macro (instance average)} \\
    Method & P@N & R@N & F1@N & mAP & P@N & R@N & F1@N & mAP \\ \hline
    Cohen \emph{s2cnn} & 0.701 & 0.711 & 0.699 & 0.676 & - & - & - & - \\
    % Cohen \emph{s2cnn\_simple} & 0.704 & 0.701 & 0.696 & 0.665 & 0.430 & 0.480 & 0.429 & 0.385\\
    Esteves \emph{sphericalcnn} & 0.717 & 0.737 & - & 0.685 & 0.450 & 0.550 & - & 0.444\\ \hline
    DeepSphere \emph{Equiangular} & 0.709 & 0.700 & 0.698 & 0.665 & 0.439 & 0.489 & 0.439 & 0.403 \\
    DeepSphere \emph{HEALPix} & 0.725 & 0.717 & 0.715 & 0.686 & 0.475 & 0.508 & 0.468 & 0.428\\
    DeepSphere \emph{Improved HEALPix} & & & & &
    \end{tabular}
    \caption{Performance of different models over SHREC17 perturbed dataset as a retrieval task, using the official script of the competition.}
    \label{tab:SHREC17_retriev}
\end{table}

\paragraph*{ModelNet 40}
\begin{table}[!ht]
    \centering
    \begin{tabular}{c|cccc}
         &  x/x & z/z & SO3/SO3 & z/SO3 \\ \hline
Cohen & 85.0 & - & - & - \\
Jiang & 90.5 & - & - & - \\
Esteves \emph{scnn} & - & 88.9 & 86.9 & 78.6 \\
%Esteves \emph{MVCNN} & 94.69 & - & - & - \\
DeepSphere & 87.8 & 86.8 & 86.7 & 76.9
    \end{tabular}
    \caption{Accuracy (in percent) on test set, for different models. The x dataset has no augmentation, the z dataset is augmented with rotation around Z-axis, and SO3 with ZYZ rotations.}
    \label{tab:mn40_results}
\end{table}
\subsubsection*{HEALPix}

HEALPix sampling, input signal at Nside = 32

@@

\subsection{climate event detection}
\subsubsection*{Results}
\begin{table}[!ht]
\begin{tabular}{l|c c c c}
        \multicolumn{1}{l}{} & \multicolumn{4}{c}{Accuracy}\\
        \cmidrule(lr){2-5}
        \multicolumn{1}{l}{Method} & TC & AR & BG & mean \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} & 94 & 93 & 97 & 94.67\\
        \cite{jiang_spherical_2019} \emph{rerun} & 93.9 & 95.7 & 95.2 & 94.95\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & 97.3 & 97.3 & 97.8 & 97.5\\
        \cite{cohen_gauge_2019} (R2R) & 97.8 & 97.4 & 97.9 & 97.7\\ \hline
        DS (weighted) & $97.4\pm 1.1$ & $97.7\pm 0.7$ & $98.2\pm 0.5$ & $97.8\pm 0.3$ \\
        DS (non-weighted) & $69.2\pm 3.7$ & $94.5\pm 2.9$ & $99.7\pm 0.1$ & $87.8\pm 0.5$ \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 97.1 & 97.6 & 96.5 & 97.1\\
        DS-Jiang (non-weighted) & 33.6 & 93.6 & 99.3 & 75.5
        % 590k
        % DeepSphere (equi non-weighted) & 99.9 & 31.3 & 75.2 & 68.80
    \end{tabular}
    \caption{Climate pattern segmentation accuracy (\%) for BG, TC
and AR classes plus mean accuracy.}
\end{table}

* DS-jiang is the similar architecture as \cite{jiang_spherical_2019}.\\

\begin{table}[!ht]
\begin{tabular}{l|c c c c c}
        \multicolumn{1}{l}{} & \multicolumn{3}{c}{Average Precision} & \multicolumn{2}{c}{Speed}\\
        \cmidrule(lr){2-4}\cmidrule(lr){5-6}
        \multicolumn{1}{l}{Method} & TC & AR & mean & inference [ms] & training \\ \hline
        %Mudigonda et al. & 97 & 74 & 65 & 78.67 & - & - & - \\
        \cite{jiang_spherical_2019} \emph{rerun} & 11.08 & 65.21 & 38.41 & 10.2 & 10h14m\\
        % 328'339
        \cite{cohen_gauge_2019} (S2R) & - & -& 68.6 & - & - \\
        \cite{cohen_gauge_2019} (R2R) & - & -& 75.9 & - & -\\ \hline
        DS (weighted) & $58.88\pm 3.17$ & $95.41\pm 1.51$ & $77.15\pm 1.94$ & 25 & 25h \\
        DS (non-weighted) & $80.86\pm 2.42$ & $97.45\pm 0.38$ & $89.16\pm 1.37$ & 30 & 13h \\ \hline
        % 12'926'432
        DS-Jiang (weighted) & 49.7 & 89.2 & 69.5 & 5 & 3h06m\\
        DS-Jiang (non-weighted) & 46.2 & 93.9 & 70.0 & 5 & 3h04m
        % 590k
        % DeepSphere (equi non-weighted) & 55.53 & 94.85 & 75.19 & 567 ms & 48h
    \end{tabular}
    \caption{Climate pattern segmentation average precision for positive classes and mean as well, plus speed performance for inference (one training pass for one instance)  and training time.}
\end{table}
\subsubsection*{Icosahedron}
icosahedron sampling, level-5 resolution

@@

30 epochs
\subsubsection*{DS-jiang}
encoder:\\
\begin{dmath}
    [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{Pool}\,+\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\, \textrm{Pool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{Pool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\,\textrm{Pool}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Pool}\,  +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L0}
\end{dmath}
decoder:\\
\begin{dmath}
    \textrm{Unpool}\, +\,[GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{concat}\, +\, [GC_{128}\, +\, BN\, +\, ReLU]_{L1}\, +\, \textrm{Unpool}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{concat}\, +\, [GC_{64}\, +\, BN\, +\, ReLU]_{L2}\, +\, \textrm{Unpool}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\, \textrm{concat}\, +\, [GC_{32}\, +\, BN\, +\, ReLU]_{L3}\, +\,\textrm{Unpool}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\,+\, \textrm{concat}\, +\, [GC_{16}\, +\, BN\, +\, ReLU]_{L4}\, +\,\textrm{Unpool}\,  +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\,+\,\textrm{concat}\, +\, [GC_{8}\, +\, BN\, +\, ReLU]_{L5}\, + \,[GC_3]_{L5}
\end{dmath}
number of parameters: 590'976  % more feat is 16 times more

@@

250 epochs with no augmentation
\subsubsection*{Results}
\begin{table}[!ht]
    \centering
    \begin{tabular}{c|ccc}
        order & MSE & MAE & R2 \\ \hline 
        0 & 10.88 & 2.42 & 0.896\\
        1 & 8.91 & 2.20 & 0.906\\
        4 & 8.20 & 2.11 & 0.919\\
        9 & 8.38 & 2.12 & 0.915\\
    \end{tabular}
    \caption{Future temperature estimation task. Evolution of performance in respect of the order of the graph filter}
    \label{tab:future_results}
    \hfill
    %~\\[1cm]
    % \begin{minipage}{0.48\linewidth}
    % \begin{tabular}{c|ccc}
    %     order & MSE & MAE & R2 \\ \hline 
    %     1 & 134.01 & 10.51 & -0.319\\
    %     4 & 129.48 & 10.31 & -0.274\\
    %     9 & 141.68 & 10.82 & -0.389\\
    % \end{tabular}
    % \caption{Baseline: testing with the present day (T-1) instead of the future day T}
    % \label{tab:present_results}
    % \end{minipage}
\end{table}

\subsubsection*{Dense}
